Transmembrane helices are also an overlooked source of major histocompatibility complex class II epitopes and evolutionary more conserved than expected by chance

### 2021-02-04 bbbq_article.tex
Progress

The definition of a binder differs from \cite{bianchi2017}:
in this study a peptide is called a binder if, within a haplotype, 
any of its 9-mer peptides have an IC50 value in the lowest 2\% of 
one thousand randomly simulated 
peptides (see table \ref{table:ic50s_per_haplotype} for values), 
whereas the original study defined
a binder as having an IC50 in the lowest 2\% of the peptides within a protein.
% See https://github.com/richelbilderbeek/bianchi_et_al_2017/blob/72e6755a31d400158368509fd80a41e984677ab1/predict-binders.R#L17

@@

Instead of using the membrane protein topology prediction
tool \verb;TMHMM; (\cite{krogh2001predicting}), PureseqTM (\cite{wang2019efficient})
is used instead.

@@

@@

\begin{figure}[!htbp]
  \includegraphics[height=0.9\textheight]{bbbq_1_fast/fig_f_tmh_mhc1_grid.png}
  \caption{
    Percentage of MHC-I epitopes overlapping with TMHs
    for a human, viral and bacterial proteome.
    The horizontal lines indicate the percentage as expected by chance.
    \richel{Refer to a table with the numbers as expected by chance)}
    See table \ref{tab:tmh_binders_mhc1} for the TMH and epitope counts.
    \richel{Epitope prediction by EpitopePrediction.}.
    Note that for smaller proteomes a percentage of zero is likelier.
    \richel{use of top 2\% binders}
  }
  \label{fig:1}
\end{figure}

@@

\begin{figure}[!htbp]
  \includegraphics[height=0.9\textheight]{bbbq_1_fast/fig_f_tmh_mhc2_grid.png}
  \caption{
    Percentage of MHC-II epitopes overlapping with TMHs
    for a human, viral and bacterial proteome.
    The horizontal lines indicate the percentage as expected by chance.
    \richel{Refer to a table with the numbers as expected by chance)}
    \richel{Epitope prediction by NetMHCIIpan.}
    See table \ref{tab:tmh_binders_mhc2} for the TMH and epitope counts.
    Note that for smaller proteomes a percentage of zero is likelier.
    \richel{use of top 2\% binders}
  }
  \label{fig:2}
\end{figure}

@@

\begin{figure}[!htbp]
  \includegraphics[width=\textwidth]{bbbq_1_fast/fig_f_tmh_mhc1_normalized.png}
  \caption{
    Normalized proportion of MHC-I epitopes overlapping with TMHs
    for human, viral and bacterial proteomes.
    Legend: covid = SARS-CoV-2, flua = influenza A, hepa = hepatitis A,
    human = homo sapiens, myco = Mycobacterium tuberculosis, 
    polio = poliovirus, rhino = rhinovirus
  }
  \label{fig:f_tmh_mhc1_normalized}
\end{figure}

@@

%\begin{table}[!htbp]
%   \input{bbbq_1_fast/bbbq_1_stats_covid.latex}
%   \caption{
%     Kolmogorov-Smirnov test results comparing human and SARS-CoV-2 for MHC-I
%     \richel{Done on the simulated data}
%   }
%   \label{table:bbbq_1_stats_covid}
% \end{table}

% \begin{table}[!htbp]
%   \input{bbbq_1_fast/bbbq_1_stats_myco.latex}
%   \caption{
%     Kolmogorov-Smirnov test results comparing human and Mycobacterium tuberculosis for MHC-I
%     \richel{Done on the simulated data}
%   }
%   \label{table:bbbq_1_stats_myco}
% \end{table}

@@

\begin{figure}[!htbp]
  \includegraphics[width=\textwidth]{bbbq_1_fast/fig_f_tmh_mhc2_normalized.png}
  \caption{
    Normalized proportion of MHC-II epitopes overlapping with TMHs
    for human, viral and bacterial proteomes.
    Legend: covid = SARS-CoV-2, flua = influenza A, hepa = hepatitis A,
    human = homo sapiens, myco = Mycobacterium tuberculosis, 
    polio = poliovirus, rhino = rhinovirus
  }
  \label{fig:f_tmh_mhc2_normalized}
\end{figure}

%\begin{sidewaystable}
%  \centering
  \input{bbbq_1_fast/table_tmh_binders_mhc2.latex}
%\end{sidewaystable}

% \begin{table}[!htbp]
%   \input{bbbq_1_fast/bbbq_2_stats_covid.latex}
%   \caption{
%     Kolmogorov-Smirnov test results comparing human and SARS-CoV-2 for MHC-II
%     \richel{Done on the simulated data}
%   }
%   \label{table:bbbq_2_stats_covid}
% \end{table}

% \begin{table}[!htbp]
%   \input{bbbq_1_fast/bbbq_2_stats_myco.latex}
%   \caption{
%     Kolmogorov-Smirnov test results comparing human and 
      Mycobacterium tuberculosis for MHC-II
%     \richel{Done on the simulated data}
%   }
%   \label{table:bbbq_2_stats_myco}
% \end{table}

>>>>

The definition of a binder differs from \cite{bianchi2017}:
in this study a peptide is called a binder if, within a haplotype, 
any of its 9-mer peptides have an IC50 value in the lowest 2\% of 
the epitopes within a proteome (see table \ref{table:ic50s_per_haplotype} for values), 
whereas the original study defined
a binder as having an IC50 in the lowest 2\% of the peptides within a protein.
% See https://github.com/richelbilderbeek/bianchi_et_al_2017/blob/72e6755a31d400158368509fd80a41e984677ab1/predict-binders.R#L17

@@

@@

% tab:elution
\input{../bbbq_article_issue_157/results/results.tex}

Table \ref{tab:elution} shows the percentage of epitopes derived from a TMH
found in the two elution studies, for the two different kind of topology
prediction tools. Whatever the tool or MHC class, at least 100 epitopes

@@

\begin{figure}[!htbp]
  \includegraphics[height=0.9\textheight]{../bbbq_1_smart/fig_f_tmh_mhc1_grid.png}
  \caption{
    Percentage of MHC-I epitopes overlapping with TMHs
    for a human, viral and bacterial proteome.
    The horizontal lines indicate the percentage as expected by chance.
    \richel{Refer to a table with the numbers as expected by chance)}
    See table \ref{tab:tmh_binders_mhc1} for the TMH and epitope counts.
    \richel{Epitope prediction by EpitopePrediction.}.
    Note that for smaller proteomes a percentage of zero is likelier.
    \richel{use of top 2\% binders}
  }
  \label{fig:1}
\end{figure}

@@

\begin{figure}[!htbp]
  \includegraphics[height=0.9\textheight]{../bbbq_1_smart/fig_f_tmh_mhc2_grid.png}
  \caption{
    Percentage of MHC-II epitopes overlapping with TMHs
    for a human, viral and bacterial proteome.
    The horizontal lines indicate the percentage as expected by chance.
    \richel{Refer to a table with the numbers as expected by chance)}
    \richel{Epitope prediction by NetMHCIIpan.}
    See table \ref{tab:tmh_binders_mhc2} for the TMH and epitope counts.
    Note that for smaller proteomes a percentage of zero is likelier.
    \richel{use of top 2\% binders}
  }
  \label{fig:2}
\end{figure}

@@

\begin{figure}[!htbp]
  \includegraphics[width=\textwidth]{../bbbq_1_smart/fig_f_tmh_mhc1_normalized.png}
  \caption{
    Normalized proportion of MHC-I epitopes overlapping with TMHs
    for human, viral and bacterial proteomes.
    Legend: covid = SARS-CoV-2, flua = influenza A, hepa = hepatitis A,
    human = homo sapiens, myco = Mycobacterium tuberculosis, 
    polio = poliovirus, rhino = rhinovirus
  }
  \label{fig:f_tmh_mhc1_normalized}
\end{figure}

@@

@@

\begin{figure}[!htbp]
  \includegraphics[width=\textwidth]{../bbbq_1_smart/fig_f_tmh_mhc2_normalized.png}
  \caption{
    Normalized proportion of MHC-II epitopes overlapping with TMHs
    for human, viral and bacterial proteomes.
    Legend: covid = SARS-CoV-2, flua = influenza A, hepa = hepatitis A,
    human = homo sapiens, myco = Mycobacterium tuberculosis, 
    polio = poliovirus, rhino = rhinovirus
  }
  \label{fig:f_tmh_mhc2_normalized}
\end{figure}

%\begin{sidewaystable}
%  \centering
%  \input{../bbbq_1_smart/table_tmh_binders_mhc2.latex}
%\end{sidewaystable}
